\begin{thebibliography}{00}

% [1] Stolojescu (IoT Smart Home)
\bibitem{yar2021edge}
H. Yar, A. S. Imran, Z. A. Khan, M. Sajjad, and Z. Kastrati, ``Towards smart home automation using IoT-enabled edge-computing paradigm,'' \textit{Sensors}, vol. 21, no. 14, Art. no. 4932, 2021.

% [2] Stolojescu (Introduction - IoT Smart Home)
\bibitem{stolojescu2021iot}
C. Stolojescu-Crisan, C. Crisan, and B.-P. Butunoi, ``An IoT-based smart home automation system,'' \textit{Sensors}, vol. 21, no. 3784, pp. 2--3, 2021.

% [3] Kurian (Related Work - Visual Gesture)
\bibitem{kurian2023visual}
B. Kurian, J. Regi, D. John, H. P., and T. Y. Mahesh, ``Visual gesture-based home automation,'' in \textit{Proc. Int. Conf. Adv. Comput. Commun. Embedded Secure Syst. (ACCESS)}, Ernakulam, India, 2023.

% [13] Wang (Introduction - Edge Computing & Privacy)
\bibitem{wang2020convergence}
X. Wang, Y. Han, V. C. M. Leung, D. Niyato, X. Yan, and X. Nan, ``Convergence of edge computing and deep learning: A comprehensive survey,'' \textit{IEEE Communications Surveys \& Tutorials}, vol. 22, no. 2, pp. 869--904, 2020.

% [20] Yu et al. (Gesture Recognition on Raspberry Pi) - 2024
\bibitem{yu2024realtime}
A. Yu, C. Qian, and Y. Guo, ``A real-time hand gesture recognition system on Raspberry Pi: A deep learning-based approach,'' in \textit{Proc. IEEE 21st Consum. Commun. Netw. Conf. (CCNC)}, Las Vegas, NV, USA, 2024, pp. 1--6.

% [4] Sengupta (Introduction - Deep Learning Review)
\bibitem{sengupta2020review}
S. Sengupta \textit{et al.}, ``A review of deep learning with special emphasis on architectures, applications and recent trends,'' \textit{IEEE Access}, vol. 8, pp. 189481--189527, 2020.

% [5] Gurrala (Related Work - LSTM)
\bibitem{gurrala2025lstm}
V. K. Gurrala, S. Talasila, R. Vaishnavi, J. Shruthi, and J. Supreeth, ``Real time hand gesture recognition using LSTM based deep learning,'' in \textit{Proc. Int. Conf. Electron. Mater. Eng. Nano-Technol. (IEMENTech)}, Kolkata, India, 2025.

% [6] Hidayat (Related Work - Rival Terdekat)
\bibitem{lopes2026geco}
M. C. Lopes \textit{et al.}, ``GECO: A real-time computer vision-assisted gesture controller for advanced IoT home system,'' \textit{Sensors}, vol. 26, no. 1, Art. no. 61, 2025.

% 7 [Google MediaPipe Documentation]
\bibitem{han2022mediapipe}
J.-S. Han, C.-I. Lee, Y.-H. Youn, and S.-J. Kim, ``A study on real-time hand gesture recognition technology by machine learning-based MediaPipe,'' \textit{Journal of System and Management Sciences}, vol. 12, no. 2, pp. 462--476, 2022.

% [15] Yu et al. (Stacked LSTM / RNN Review) - 2019
\bibitem{yu2019review}
Y. Yu, X. Si, C. Hu, and J. Zhang, ``A review of recurrent neural networks: LSTM cells and network architectures,'' \textit{Neural Computation}, vol. 31, no. 7, pp. 1235--1270, 2019.

% [16] Labach et al. (Dropout Survey) - 2019
\bibitem{labach2019survey}
N. Labach, H. Salehinejad, and S. Valaee, ``Survey of dropout methods for deep learning,'' \textit{arXiv preprint arXiv:1904.13310}, 2019.

% [17] Dubey et al. (Activation Functions) - 2022
\bibitem{dubey2022activation}
S. R. Dubey, S. K. Singh, and B. B. Chaudhuri, ``Activation functions in deep learning: A comprehensive survey and benchmark,'' \textit{Neurocomputing}, vol. 503, pp. 92--108, 2022.

% [14] David et al. (TFLite Micro)
\bibitem{david2021tflite}
R. David \textit{et al.}, ``TFLite Micro: Embedded machine learning on tiny devices,'' \textit{Proceedings of Machine Learning and Systems}, vol. 3, pp. 1--11, 2021.

% [8] TFLite Docs (Method - Optimization)
\bibitem{orasan2022quantization}
I. L. Orăşan, C. Seiculescu, and C. D. Caleanu, ``Benchmarking TensorFlow Lite quantization algorithms for deep neural networks,'' in \textit{Proc. IEEE 16th Int. Symp. Appl. Comput. Intell. Informat. (SACI)}, 2022, pp. 221--226.

% 10 [Docker]
\bibitem{potdar2020docker}
A. M. Potdar, D. G. Narayan, S. Kengond, and M. M. Mulla, ``Performance evaluation of Docker container and virtual machine,'' \textit{Procedia Computer Science}, vol. 171, pp. 1419--1428, 2020.

% [18] Noparlik & Zdunek (State Machine Logic) - 2023
\bibitem{noparlik2023hand}
R. Noparlik and R. Zdunek, ``Hand gesture recognition system with finite state machine for remote desktop control,'' in \textit{Proc. 8th Int. Conf. Smart Sustainable Technol. (SpliTech)}, Split, Croatia, 2023, pp. 1--6.

% [12] Grandini (Evaluation Metrics Overview)
\bibitem{grandini2020metrics}
M. Grandini, E. Bagli, and G. Visani, ``Metrics for multi-class classification: An overview,'' \textit{arXiv preprint arXiv:2008.05756}, 2020.

% [11] Attig (Discussion - Latency Guidelines)
\bibitem{Attig_LatencyGuidelines}
C. Attig, N. Rauh, T. Franke, and J. F. Krems, ``System latency guidelines then and now -- Is zero latency really considered necessary?'' in \textit{Engineering Psychology and Cognitive Ergonomics}, vol. 10276, D. Harris, Ed. Cham, Switzerland: Springer, 2017, pp. 2--14.

\end{thebibliography}